Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
merging
RQ1

\newcommand{\numNonContentAttacks}{4}
\newcommand{\numContentAttacks}{10}

@@

RQ1 addresses the performance of \tname. The metric we use is the
position of the golden rule at the ranked list of plausible rules
reported by \tname\ (see Figure~\ref{fig:overview}). This metric is a
proxy of human performance in analyzing the list of plausible rules.

@@

Table~\ref{table:results} shows results. Column ``Name'' shows the
name of the attack, column ``\#~Vars.'' shows the number of variants
of the attack, column ``\#~Option Cand. (step 1)'' shows the number of
option candidates reported by \tname\ at step 1, column ``\#~Plausible
Rules (step 2)'' shows the number of plausible rules reported by
\tname\ at step 2, and column ``Rank (step 3)'' shows the position of the
golden rule in the ranked list reported at step 3.
It is important to indicate that column ``\#~Vars.'' shows the input of
\tname\ that varies across different attacks. Although \tname\ also
depends on the data sets of benign traffic and existing \suri\ rules,
these inputs are constant across different executions of the tool. The
rest of the columns show the progress of the tool at various stages
and provide an indication of complexity of the synthesis problem.

@@

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top ten rules of the ranking in
\percTopFiveRanking\ of the cases.

@@

\emph{ \textbf{Summary of results:}~\tname\ successfully synthesizes
  the golden rules in all cases and that rule is ranked among the top
  ten rules in \percTopFiveRanking\ of the cases.  }

>>>>

@@

RQ1 assesses \tname's performance. The metric we use is the position
of the golden rule at the ranked list of plausible rules reported by
\tname\ (see Figure~\ref{fig:overview}). This metric is a proxy of
human performance in analyzing the list of plausible rules.

@@

Table~\ref{table:results} shows results. Column ``Name'' shows the
name of the attack, column ``\#~Vars.'' shows the number of variants
of the attack, column ``\#~Option Cand. (step~1)'' shows the number of
option candidates reported by \tname\ at step 1, column ``\#~Plausible
Rules (step~2)'' shows the number of rules reported by \tname\ at step
2, and column ``Rank (step~3)'' shows the position of the golden rule
in the reported ranking.  Column ``\#~Vars.''  shows the number of
variants of a given attack. The other data that \tname\ depends upon
are not mentioned as they are constant. The rest of the columns show
the progress of the tool at various stages and provide an indication
of complexity of the synthesis problem.

@@

Overall, results show that \tname\ performed very well in most of the
cases. It reported the ground truth rule in \emph{all} cases and
reported that rule within the top-1, top-3, top-5, and top-10 rules of
the ranking, respectively, in \percTopOneRanking\,
\percTopThreeRanking, \percTopFiveRanking, and \percTopTenRanking\ of
the cases.

@@

\emph{ \textbf{Summary of results:}~\tname\ successfully synthesizes
  the golden rules in all cases and that rule is ranked among the top
  three rules of the ranking in \percTopThreeRanking\ of the cases.  }
